Iterative forecasting and the trap of self-fulfilling prophecies

### 2021-04-06 manuscript/manuscript.Rmd
formatting

header-includes:
  - \linenumbers

csl: csl/ecology-letters.csl
output: rticles::elsevier_article
layout: 3p
journal: TBD
---

>>>>

header-includes:
  - \linenumbers
  - \usepackage{endfloat}

csl: csl/ecology-letters.csl
output: rticles::elsevier_article
layout: 3p
journal: Ecology Letters
---

- abbreviated running title: "The trap of self-fulfilling prophecies"
- Authorship statement: _This is a single-author paper_
- data accessibility statement: _All simulation data generated for analyses here, along with code required for the analysis, is available in the Zenodo Data archive, https://doi.org/10.5281/zenodo.4660621_
- number of words in the abstract: 116
- number of words in main text: 4998
- number of cited references: 33
- number of tables & figures: 4 Figures
